\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-19 doc/publications/plos16/plos16.tex
added figure for run comparison and commented out table

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{\cursedforest - A Random Forest Implementation for ``Big'' and ``Wide'' Data} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Aidan O'Brien\textsuperscript{1},
Piotr Szul\textsuperscript{2},
Stephanie Li\textsuperscript{3},
James Doecke\textsuperscript{3},
Nick Ellis\textsuperscript{4},
Robert Dunne\textsuperscript{5}, and
Denis C. Bauer\textsuperscript{1,*}
%, with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Health \& Biosecurity, CSIRO, Sydney, NSW, Australia
\\
\textbf{2} Data61, CSIRO, Brisbane, QLD, Australia
\\
\textbf{3} Health \& Biosecurity, CSIRO, Brisbane, QLD, Australia
\\
\textbf{4} Oceans \& Atmosphere, CSIRO, Brisbane, QLD, Australia
\\
\textbf{5} Data61, CSIRO, Sydney, NSW, Australia
\\
\bigskip

@@

@@

\multirow{5}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest & 0.04  & 1 min 50 seconds                        \\
                                                & Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & \randomforest (R)         & 0.05       & 24 min           \\
                                                & \ranger (R)      & 0.06       & 1 min 10 seconds       \\
                                                & \ranger (C++)     & 0.06       & 7 min            \\
                                                & H2O           & ??       & ??         \\

@@

\multirow{5}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest & 0.06 & 4 min 2 seconds \\
                                                    & Spark ML  & 0.06 & 37 min 19 seconds \\
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)    & 0.06       & 4 min 30 seconds     \\
                                                    & \ranger (C++)     &     ??   & ??        \\
                                                    & H2O           & 0.05       & 16 hours         \\

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest & 0.04  & 19 min 19 seconds         \\
                                                    & Spark ML  & 0.04       & 8 hour 29 min        \\
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)      &  0.05       & 28 mins         \\
                                                    & \ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest & 0.02  & 56 min 43 seconds             \\
                                                    & Spark ML &    NA         &   NA               \\
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)      & 0.03      &    3 hour 58 min     \\
                                                    & \ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest & 0.01  & 3hour 16min \\
                                                    & Spark ML & NA & NA  \\
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)       &        NA     &        NA    \\
                                                    & \ranger (C++)       &        NA     &        NA    \\
                                                    & H2O           & NA       & NA         \\
\hline

@@

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{\cursedforest - A Random Forest Implementation for ``Big'' and ``Wide'' Data} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Aidan O'Brien\textsuperscript{1},
Piotr Szul\textsuperscript{2},
Robert Dunne\textsuperscript{3}, 
Paul Leo \textsuperscript{4},
Emma L. Duncan \textsuperscript{4,5,6},
Stephanie Li\textsuperscript{7},
James Doecke\textsuperscript{7},
Nick Ellis\textsuperscript{8}, and
Denis C. Bauer\textsuperscript{1,*}
%, with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Health \& Biosecurity, CSIRO, Sydney, NSW, Australia
\\
\textbf{2} Data61, CSIRO, Brisbane, QLD, Australia
\\
\textbf{3} Data61, CSIRO, Sydney, NSW, Australia
\\
\textbf{4} Institute of Health and Biomedical Innovation, Queensland University of Technology, Brisbane, QLD, Australia
\\
\textbf{5} Department of Endocrinology, Royal Brisbane and Women's Hospital, Brisbane, QLD, Australia
\\
\textbf{6} Faculty of Medicine and Biomedical Sciences, University of Queensland, Brisbane, QLD, Australia
\\
\textbf{7} Health \& Biosecurity, CSIRO, Brisbane, QLD, Australia
\\
\textbf{8} Oceans \& Atmosphere, CSIRO, Brisbane, QLD, Australia
\bigskip

@@

\begin{figure}[tbhp] 
    \caption{\textbf{Runtime comparison on the 1000 genomes project}} 
    \label{figure:synth1}
      \includegraphics[totalheight=8cm]{./figs/1000genomesRuntime.pdf}
    \begin{flushleft} 
      The figure shows the runtime for the 5 subsets of the 1000 genomes project and the different methods investigated. $\bigotimes$ marks the last dataset the different method completed before running out of memory or running more than 24 hours. The dashed lines mark the trajectory for how ranger and SparkML had performed given larger memory machines. 
    \end{flushleft}
\end{figure}

\iffalse

@@

\multirow{5}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest & 0.04  & 1 min 50 seconds    \\ %110
                                                & Spark ML  &  0.05           &           7 min 44 seconds         \\  %464
                                                & \randomforest (R)         & 0.05       & 24 min           \\ %1440
                                                & \ranger (R)      & 0.06       & 1 min 10 seconds       \\ %70
                                                & \ranger (C++)     & 0.06       & 7 min            \\ %420
                                                & H2O           & ??       & ??         \\

@@

\multirow{5}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest & 0.06 & 4 min 2 seconds \\  %240
                                                    & Spark ML  & 0.06 & 37 min 19 seconds \\  %2239
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)    & 0.06       & 4 min 30 seconds     \\  %270
                                                    & \ranger (C++)     &     ??   & ??        \\
                                                    & H2O           & 0.05       & 16 hours         \\ %57600

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest & 0.04  & 19 min 19 seconds         \\ %1159
                                                    & Spark ML  & 0.04       & 8 hour 29 min        \\ % 3403
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)      &  0.05       & 28 mins         \\ %1680
                                                    & \ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest & 0.02  & 56 min 43 seconds             \\ %3403
                                                    & Spark ML &    NA         &   NA               \\ %30540
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)      & 0.03      &    3 hour 58 min     \\ %14280
                                                    & \ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest & 0.01  & 3hour 16min \\ %11760
                                                    & Spark ML & NA & NA  \\
                                                    & \randomforest (R)        & NA         & NA                \\
                                                    & \ranger (R)       &        NA     &        NA    \\
                                                    & \ranger (C++)       &        NA     &        NA    \\
                                                    & H2O           & NA       & NA         \\
\hline

@@

\fi
